SciPy - some descriptive title here

### 2018-06-28 scipy-1.0/paper.tex
Tidy text:
- Address edits from reviews
- Make a note where current thinking may be flawed (further research required)
- Add caption to figure (needs some work, but better than nothing)

\documentclass[fleqn,10pt]{wlscirep}

@@

@@

% need some better usage stats sources?
% SciPy stuff from njs blog: https://docs.google.com/spreadsheets/d/1lOLvSF0up4eZyv2ugZi-TM_GIs3gPCkGNIDKXS1Y3w4/edit#gid=406031940
From the user side, there have been at least 15 million downloads
of the SciPy manylinux wheels between the start of 2016 and May of 2018
(njs blog). The recommended source for citing SciPy is simply a reference
to the website / library itself\cite{SciPylib}, and has been cited $>3000$
times. Some of the most prominent citing articles include the IPython
publication\cite{PER-GRA:2007}, a heavily-cited Nature Biotechnology
article\cite{pmid17287757}, a dark
matter annihilitation study in the field of
cosmology\cite{1475-7516-2012-08-007}, and many of the
other major downstream software libraries in the Python scientific
computing stack.

@@

>>>>

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[fleqn,10pt]{wlscirep}

@@

\usepackage[dvipsnames]{xcolor}
\usepackage{todonotes}
\presetkeys%
    {todonotes}%
    {inline,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum}{}

@@

% need some better usage stats sources?
%
% note: @stefanv has pypinfo set up, so can grab all the info shown at
% https://github.com/ofek/pypinfo
%
% SciPy stuff from njs blog: https://docs.google.com/spreadsheets/d/1lOLvSF0up4eZyv2ugZi-TM_GIs3gPCkGNIDKXS1Y3w4/edit#gid=406031940
From the user side, there have been at least 15 million downloads
of the SciPy manylinux wheels between the start of 2016 and May of 2018
(njs blog). The recommended manuscript for citing SciPy,
published online 17 years ago, has been cited $>3000$
times. Some of the most prominent citing articles include the IPython
publication, a heavily-cited Nature Biotechnology article, a dark
matter annihlitation study in the field of cosmology, and many of the
other major downstream software libraries in the Python scientific
computing stack.

@@

\subsection*{ndimage pixel vs point}

\begin{itemize}
  \item A pixel is not a little square
    (http://alvyray.com/Memos/CG/Microsoft/6\_pixel.pdf)
  \item Match edges vs match centers
    (http://entropymine.com/imageworsener/matching/)
\end{itemize}

There are two competing models for representing image measurements:
the first considers an image as a collection of pixels, square blocks
of size 1x1 with centers offset by (0.5, 0.5).  This model corresponds
closely with a camera sensor, that integrates light as it falls on
(more-or-less) square elements, producing a digital readout for each.

Another view is that of an image as a grid of point measurements.
This model explicitly rejects two notions encouraged by the pixel
model: that our signal is best represented as a step-wise function, and
that a single measurement represents knowledge of the surrounding
square area element.  Instead, we think of the image as a smoothly
varying function, of which we have measurements at grid positions.

While the representations may not seem very different, they have
significant implications for image processing algorithms such as
rescaling.

{\tt ndimage} currently follows the pixel model for operations like
{\tt zoom} but the data point model for general geometric
transformations and interpolation.  We think that consistently using
the data point model will serve us better in the long run:

\begin{enumerate}
  \item It makes no assumption about the sampling mechanism used
    (camera, scanner, laser, etc.).
  \item NumPy coordinates map directly to measurement coordinates,
    without a 0.5 offset. \todo{Will have to rethink this statement,
      since this {\bf is} the current underlying model for interpolation}
  \item It makes it easier to reason about extrapolation.  E.g., the current
    dubious notion of ``reflection'', in which the image is padded
    {\tt d c b a | a b c d | d c b a} becomes nonsensical, and leaves
    only the reliable notion of mirroring, {\tt d c b | a b c d | c b a}.
\end{enumerate}

The second model, while consistent, does introduce some challenges
w.r.t. traditional image manipulation (see attached figure).

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{static/image_pixel_model}
    \caption{Upscaling an image 2x.  In the data point model, the
      original data points remain in the image corners, which means it
      contributes less to the center of the resulting image than to
      the corners.  In the pixel model, the original pixels contribute
      more evenly to both of these.}
    \label{fig:image-pixel-model}
\end{figure}
